---
title: "Final Report"
author: "Jane Huber"
date: "3/28/2022"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    theme: sandstone
    number_sections: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, verbose = FALSE)

library(tidyverse)
library(lubridate)
library(parsnip)
library(cmfproperty)
library(purrr)
library(gridExtra)
library(ggplot2)
library(tidymodels)
library(glmnet)
library(leaflet)
library(sf)
library(simplevis)
library(xgboost)
library(finetune)
library(tune)
library(baguette)
library(kernlab)

theme_set(theme_bw())
```

```{r download-data-and-clean, include=FALSE}


custom_theme <- theme_bw() +
  theme(plot.title = element_text(size = 9),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9))

# property_classifications <- read_xlsx("files/OFFICE OF THE ASSESSORS_PROPERTY CLASSIFICATIONS -rev.xlsx")

years_for_evaluation <- c('2016', '2017', '2018', '2019')

con <- DBI::dbConnect(RSQLite::SQLite(), "../database/detroit.sqlite")

# convert to tibble
sales <- dplyr::tbl(con, 'sales') %>% dplyr::collect()

#remove factor for sale date
sales_clean <- 
  sales %>% 
  select(c(parcel_num, sale_date, sale_price, sale_terms, property_c)) %>% 
  rename(c(prop_class = property_c)) %>% 
  mutate(sale_date = format(as.Date(sale_date), format="%Y"),
         sale_terms = str_replace_all(sale_terms, "Not Arms Length", "NOT ARMS LENGTH"),
         sale_terms = str_replace_all(sale_terms, "not arms length", "NOT ARMS LENGTH"),
         sale_terms = str_replace_all(sale_terms, "valid arms length", "VALID ARMS LENGTH"),
         sale_terms = str_replace_all(sale_terms, "Valid Arms Length", "VALID ARMS LENGTH"),
         sale_terms = str_replace_all(sale_terms, "bank sale used", "BANK SALE USED"),
         sale_terms = str_replace_all(sale_terms, "00-NOT AUDITED", "NOT AUDITED"),
         prop_class = as_factor(prop_class), 
         sale_terms = as_factor(sale_terms)) %>% 
  filter(sale_terms == "VALID ARMS LENGTH",
         sale_date %in% years_for_evaluation,
         prop_class == '401')

rm(sales)
invisible(gc())

# Assessments
assessments <- dplyr::tbl(con, 'assessments') %>% dplyr::collect()

assessments_clean <-
  assessments %>%
  rename(c(parcel_num = PARCELNO,
           assessed_value = ASSESSEDVALUE,
           taxable_value = TAXABLEVALUE,
           assessment_year = year,
           prop_class = propclass)) %>% 
  mutate(prop_class = as_factor(prop_class)) %>% 
  filter(assessed_value > 2000)

rm(assessments)
invisible(gc())

# Parcels: Create a parcels tibble that combines historic with all. Can filter down later if needed.
parcels <- dplyr::tbl(con, 'parcels') %>% dplyr::collect()

parcels_current_clean <-
  parcels %>%
  rename(parcel_num = parcel_number) %>%
  mutate(zip_code = as.numeric(zip_code),
         property_class = as.factor(property_class))

rm(parcels)
invisible(gc())

parcels_historic <- dplyr::tbl(con, 'parcels_historic') %>% dplyr::collect()

parcels_historic_clean <-
  parcels_historic %>%
  rename(parcel_num = PARCELNO,
         address = PROPADDR,
         zip_code = ZIPCODE,
         taxpayer_1 = TAXPAYER1,
         taxpayer_street = TAXPADDR,
         taxpayer_city = TAXPCITY,
         taxpayer_state = TAXPSTATE,
         taxpayer_zip = TAXPZIP,
         property_class = propclass,
         tax_status = TAXSTATUS,
         total_square_footage = TOTALSQFT,
         total_acreage = TOTALACREAGE,
         frontage = FRONTAGE,
         homestead_pre = PRE,
         sale_price = SALEPRICE,
         sale_date = SALEDATE,
         assessed_value = ASSESSEDVALUE,
         taxable_value = TAXABLEVALUE) %>%
  mutate(zip_code = as.numeric(zip_code),
         property_class = as.factor(property_class)) %>% 
  filter(!is.na(total_square_footage))

rm(parcels_historic)
invisible(gc())

parcels_clean <-
  left_join(parcels_current_clean, parcels_historic_clean) %>% 
  select(c(ward, parcel_num, council_district, zip_code, total_square_footage, X, Y)) %>% 
  mutate(zip_code = as.numeric(zip_code))

rm(list='parcels_current_clean', 'parcels_historic_clean')
invisible(gc())

#Attributes
attributes <- dplyr::tbl(con, 'attributes') %>% dplyr::collect()
attributes_clean <- 
  attributes %>% 
  rename(neighborhood = Neighborhood,
         total_square_footage = total_squa,
         assessed_value = assessed_v,
         taxable_value = taxable_va,
         sale_price = 'Sale Price',
         sale_date = 'SALE_YEAR',
         total_floors = total_floo,
         prop_class = property_c) %>% 
  select(!c(st_num, st_name, taxpayer_1, use_code_d, homestead_, 'Sale Date', heightcat, Longitude, Latitude))  %>% 
  mutate(prop_class = as_factor(prop_class))

rm(attributes)
invisible(gc())


# Combine sales and assessments
sales_and_assessments <- 
  left_join(sales_clean, assessments_clean) %>% 
  filter(!is.na(sale_date)) %>% 
  mutate(sale_date = as.numeric(sale_date))

rm(list='sales_clean', 'assessments_clean')
invisible(gc())

#Combine sales, assessments, parcels
sales_assessments_parcels <- 
  left_join(sales_and_assessments, parcels_clean) 

rm(list='sales_and_assessments', 'parcels_clean')
invisible(gc())


sales_assessments_parcels_attributes <- 
  left_join(sales_assessments_parcels, attributes_clean)

rm(list='sales_assessments_parcels', 'attributes_clean')
invisible(gc())
  
#Foreclosures
foreclosures <- dplyr::tbl(con, 'foreclosures') %>% dplyr::collect()
foreclosures_clean <- 
  foreclosures %>% 
  rename(address = prop_addr,
         parcel_num = prop_parcelnum) %>% 
  select(c(address, parcel_num, years_for_evaluation)) %>% 
  pivot_longer(cols = years_for_evaluation,
               names_to = "foreclosure_year",
               values_to = "foreclosed",
               values_drop_na = TRUE) %>% 
  select(parcel_num, foreclosed)

rm(foreclosures)
invisible(gc())

#Finally create full dataset

full_dataset <- 
  left_join(sales_assessments_parcels_attributes, foreclosures_clean)

rm(list='sales_assessments_parcels_attributes', 'foreclosures_clean')
invisible(gc())

#Final cleanup--remove initial tibbles from SQLite now that we've filtered for the data we actually want

rm(list = 'con', 'years_for_evaluation')
invisible(gc())

```


# Introduction

Homes in Detroit have suffered from poorly assessed home values, which has contributed greatly to foreclosure during a time of economic instability. The UC Irvine Law Review's ["Taxed Out: Illegal Property Tax Assessments and the Epidemic of Tax Foreclosures in Detroit"](https://scholarship.law.uci.edu/ucilr/vol9/iss4/3/) analyzes  the relationship between over-assessing a home and its role in driving foreclosures, exposing government's role in creating conditions for people to lose their homes. The Harris School of Public Policy at the University of Chicago's The Center For Municipal Finance produced the report ["An Evaluation of Residential Property Tax Assessments in the City of Detroit, 2016-2018"](https://harris.uchicago.edu/files/evalrespropertytaxasdetroit20162018.pdf) shows how the city of Detroit attempted to correct that mistake, reducing the number of assessments higher than sales, but that it's still too high.

```{r cmfproperty-sales-ratio, include=FALSE}
ratios <-
  invisible(
  cmfproperty::reformat_data(
    data = full_dataset,
    sale_col = "sale_price",
    assessment_col = "assessed_value",
    sale_year_col = "sale_date",
  ))

stats <- cmfproperty::calc_iaao_stats(ratios)

output <- diagnostic_plots(stats,
                           ratios,
                           min_reporting_yr = 2016,
                           max_reporting_yr = 2019)
```

```{r display-grid, message = FALSE, warning = FALSE, echo = FALSE, verbose = FALSE}
grid.arrange(output[[3]], output[[2]], ncol = 1)

rm(list = 'stats', 'ratio', 'output')
invisible(gc())

```



Detroit’s assessment values across percentile home values appear to have remained steady in dollars since 2016, even as home assessments increased over time. It is important to note, however, that the red line (homes at the 25th percentile of sale price) have the smallest gap between their assessed value and their sale price. This helps us to see the way in which inequality has been exacerbated by assessing homes at a much closer value to their sale price than for more expensive homes.



# New Assessment Models (Part A)

When evaluating over-assessments for homes in Detroit, using 2016 as a year to generate a model predicting the likelihood of over-assessments, we test a base model that evaluates the impact of ward, sale price, zip code, and  the total square footage of a home. Then, we compare the results by adding in more nuanced predictors, such as the percent of home foreclosures in a zip code and the average sale price of a home in the zip code. Perhaps not surprisingly, adding in these more nuanced variables made for a more effective model. In addition to this work, 

```{r first-model-overassessment, include=TRUE}

# Get data filtered
overassessed <- 
full_dataset %>% 
  mutate(overassessed = as_factor(if_else(sale_price < (assessed_value * 2),
                                "YES",
                                "NO")))

overassessed_2016_sales <- 
  overassessed %>% 
    filter(sale_date == 2016,
         assessment_year == 2016) %>% 
  mutate(log_sale_price = log(sale_price),
         log_assessed_value = log(assessed_value)) %>% 
  filter(!is.na(ward),
         !is.na(sale_price),
         !is.na(zip_code),
         !is.na(total_square_footage))

split <- rsample::initial_split(overassessed_2016_sales)

train <- training(split)
test <- testing(split)

log_model <- 
  logistic_reg() %>%
  set_engine('glm') %>%
  set_mode('classification')

overassessed_first_recipe <- 
  recipe(overassessed ~ ward + sale_price + zip_code + total_square_footage,
      data = train) %>%
  step_other(ward, threshold = 0.01) %>% 
  step_other(zip_code, threshold = 0.01) %>% 
  step_dummy(all_nominal_predictors())
  
overassessed_workflow <- 
  workflow() %>%
  add_model(log_model) %>% 
  add_recipe(overassessed_first_recipe)


#Evaluate model
rf_fit <- fit(overassessed_workflow, overassessed_2016_sales)

homes_2016 <- 
  test %>% 
  filter(sale_date == 2016)

overassessment_predictions <- 
  augment(rf_fit, homes_2016)

rm(list='rf_fit', 'homes_2016')

overassment_evaluation <- 
  left_join(overassessment_predictions, overassessed_2016_sales) %>% 
  group_by(overassessed) %>% 
  summarize(predicted_not_overassessed = sum(.pred_class == "NO", na.rm=TRUE),
            predicted_overassessed = sum(.pred_class == "YES", na.rm = TRUE))

# Create a classifier metrics table to help us further evaluate our model.

true_negative <- overassment_evaluation$predicted_not_overassessed[1]
false_negative <- overassment_evaluation$predicted_not_overassessed[2]
false_positive <- overassment_evaluation$predicted_overassessed[1]
true_positive <- overassment_evaluation$predicted_overassessed[2]

true_positive_rate <- true_positive / (true_positive + false_negative)
true_negative_rate <- true_negative / (true_negative + false_positive)
false_positive_rate <- false_positive /(false_positive + true_negative)
false_negative_rate <- false_negative / (false_negative + true_positive)
positive_predictive_value <- true_positive / (true_positive + false_positive)

classifier_metrics_table <- tibble(measurement = c("true positive rate", 
                                                   "true negative rate",
                                                   "false positive rate",
                                                   "false negative rate",
                                                   "positive predictive value"), 
                                   initial_model = c(true_positive_rate, 
                                               true_negative_rate,
                                               false_positive_rate,
                                               false_negative_rate,
                                               positive_predictive_value))

```


```{r second-model-overassessment-and-comparison}

additional_predictor_variables <- 
  full_dataset %>% 
  filter(!is.na(zip_code)) %>% 
  group_by(zip_code) %>% 
  summarise(percent_zip_foreclosures = sum(foreclosed, na.rm=TRUE)/n(),
            avg_sale_price_zip = mean(sale_price, na.rm=TRUE)) %>% 
    filter(!is.na(percent_zip_foreclosures),
         !is.na(avg_sale_price_zip))

overassessed_with_additional_field <- 
  left_join(overassessed_2016_sales, additional_predictor_variables)

split_2 <- rsample::initial_split(overassessed_with_additional_field)

train_model_2 <- training(split_2)
test_model_2 <- testing(split_2)

# Add new field here 
overassessed_second_recipe <- 
  recipe(overassessed ~ ward + sale_price + zip_code + total_square_footage + percent_zip_foreclosures,
      data = train_model_2) %>%
  step_other(ward, threshold = 0.01) %>% 
  step_other(zip_code, threshold = 0.01) %>% 
  step_dummy(all_nominal_predictors()) 


#use old workflow with model, just remove old recipe and add new one
overassessed_workflow <- 
  overassessed_workflow %>% 
  update_recipe(overassessed_second_recipe)

rf_fit_model_2 <- 
  fit(overassessed_workflow, overassessed_with_additional_field)

homes_2016_model2 <- 
  test_model_2 %>% 
  filter(sale_date == 2016)

overassessment_predictions_model_2 <- 
  augment(rf_fit_model_2, homes_2016_model2)


overassment_evaluation_model_2 <- 
  left_join(overassessment_predictions_model_2, overassessed) %>% 
  group_by(overassessed) %>% 
  summarize(predicted_not_overassessed = sum(.pred_class == "NO", na.rm=TRUE),
            predicted_overassessed = sum(.pred_class == "YES", na.rm = TRUE))

# Create a classifier metrics table to help us further evaluate our model.

true_negative <- overassment_evaluation_model_2$predicted_not_overassessed[1]
false_negative <- overassment_evaluation_model_2$predicted_not_overassessed[2]
false_positive <- overassment_evaluation_model_2$predicted_overassessed[1]
true_positive <- overassment_evaluation_model_2$predicted_overassessed[2]

true_positive_rate <- true_positive / (true_positive + false_negative)
true_negative_rate <- true_negative / (true_negative + false_positive)
false_positive_rate <- false_positive /(false_positive + true_negative)
false_negative_rate <- false_negative / (false_negative + true_positive)
positive_predictive_value <- true_positive / (true_positive + false_positive)

classifier_metrics_table_second <- tibble(measurement = c("true positive rate", 
                                                   "true negative rate",
                                                   "false positive rate",
                                                   "false negative rate",
                                                   "positive predictive value"), 
                                   with_additional_values = c(true_positive_rate, 
                                               true_negative_rate,
                                               false_positive_rate,
                                               false_negative_rate,
                                               positive_predictive_value))

#classifier_metrics_table_second

rm(list='true_negative', 'false_negative', 'false_positive', 'true_positive',
   'true_positive_rate',
   'true_negative_rate',
   'false_positive_rate',
   'false_negative_rate',
   'positive_predictive_value')
invisible(gc())


# Table Comparing Initial Model and New Model

comparison_data_first_and_second_model <-
  left_join(classifier_metrics_table, classifier_metrics_table_second)

comparison_data_first_and_second_model

```


Stepping into the shoes of the assessor in Detroit, we also develop a model to predict sale prices of homes in Detroit, which could be used to inform assessments. By evaluating and testing on sales in the city of Detroit in 2019, we can train our model based on sales and see if we are able to effectively predict sale prices for other homes in Detroit. We follow our strategy for over-assessments, generating a base model that looks at ward, zip code, total square footage, and assessed_value. We then augment this model with the percent of home foreclosures in a zip code and the average sale price of a home in the zip code to see if it improves our model. Unlike the over-assessments, this helped to improve our model.


```{r first-model-sales-predictions}

data_for_predictions <- 
  full_dataset %>% 
  filter(sale_date == 2019,
     !is.na(zip_code),
     !is.na(total_square_footage),
     !is.na(ward),
     !is.na(assessed_value)) %>% 
  mutate(log_av = log(assessed_value))

split_sales <- 
  rsample::initial_split(data_for_predictions)


train_sales <- training(split_sales)
test_sales <- testing(split_sales)

linear_model_sales <- 
   boost_tree() %>% 
   set_engine("xgboost") %>% 
   set_mode("regression")

sale_price_recipe <- 
  recipe(sale_price ~ ward + zip_code + total_square_footage + log_av,
      data = train_sales) %>%
  step_other(ward, threshold = 0.01) %>% 
  step_other(zip_code, threshold = 0.01) %>% 
  step_unknown(all_nominal_predictors()) %>%
  step_dummy(all_nominal_predictors())

sale_wflow <- 
  workflow() %>%
  add_model(linear_model_sales) %>% 
  add_recipe(sale_price_recipe)

# Fit the model
rf_fit_sales <- fit(sale_wflow, train_sales)

sales_2019 <- 
  test_sales %>% 
  filter(sale_date == 2019)

sale_price_predictions <- 
  augment(rf_fit_sales, sales_2019)

first_prediction <- 
  yardstick::rmse(sale_price_predictions,
       truth = sale_price,
       estimate = .pred)

first_prediction_estimate <- 
  first_prediction$.estimate[1]
  
rm(first_prediction)
invisible(gc())

```

```{r second-model-sales-predictions}

sales_predictions_with_additional_dataset <- 
  left_join(full_dataset, additional_predictor_variables)

sales_predictions_with_additional_dataset_2019 <- 
  sales_predictions_with_additional_dataset %>% 
  filter(sale_date == 2019,
         !is.na(zip_code),
         !is.na(percent_zip_foreclosures),
         !is.na(avg_sale_price_zip),
         !is.na(assessed_value),
         !is.na(total_square_footage),
         !is.na(ward)) %>% 
  na.omit(sales_predictions_with_additional_dataset_2019)

split_sales_model_2 <- 
  rsample::initial_split(sales_predictions_with_additional_dataset_2019)

train_sales_2 <- training(split_sales_model_2)
test_sales_2 <- testing(split_sales_model_2)


sale_price_recipe_model_2 <- 
  recipe(sale_price ~ ward + sale_price + zip_code + assessed_value + percent_zip_foreclosures + avg_sale_price_zip,
      data = train_sales_2) %>%
  step_other(ward, threshold = 0.01) %>% 
  step_other(zip_code, threshold = 0.01) %>% 
  step_dummy(all_nominal_predictors())
  
sale_wflow <- 
  sale_wflow %>% 
  update_recipe(sale_price_recipe_model_2)

# Fit the model
rf_fit_sales_model_2 <- fit(sale_wflow, train_sales_2)

sale_price_predictions <- 
  augment(rf_fit_sales_model_2, test_sales_2)

#Now, compare initial model with this model

second_prediction <- 
  yardstick::rmse(sale_price_predictions,
       truth = sale_price,
       estimate = .pred)

second_prediction_estimate <- 
  second_prediction$.estimate[1]


# all_predictions <- 
#   tibble(first_RMSE = first_prediction_estimate,
#          second_RMSE = second_prediction_estimate)
#   
# all_predictions
```

# Comparison

In developing these models, we used GLM and experimented with adding more predictors to create a more accurate model. However, we can further explore how to best predict sale price by comparing different types of models and tuning them. Below, we will compare linear regression, random forests, XG Boost model, and a K-Nearest Neighbor model to see which performs the best.


```{r comparing-sales-models}

linear_reg_spec <- 
   linear_reg(penalty = tune(), mixture = tune()) %>% 
   set_engine("glmnet")

rf_spec <- 
   rand_forest(mtry = tune(), min_n = tune(), trees = 1000) %>% 
   set_engine("ranger") %>% 
   set_mode("regression")
   
xgb_spec <- 
   boost_tree(tree_depth = tune(), learn_rate = tune(), loss_reduction = tune(), 
              min_n = tune(), sample_size = tune(), trees = tune()) %>% 
   set_engine("xgboost") %>% 
   set_mode("regression")

knn_spec <- 
   nearest_neighbor(neighbors = tune(), dist_power = tune(), weight_func = tune()) %>% 
   set_engine("kknn") %>% 
   set_mode("regression")
   

# Update my recipe here:
updated_recipe <- 
  sale_price_recipe_model_2 %>% 
  step_YeoJohnson(all_numeric_predictors()) %>% 
  step_normalize(all_numeric_predictors()) %>% 
  step_pca(all_numeric_predictors(), num_comp = tune()) %>% 
  step_normalize(all_numeric_predictors())

my_set <- workflow_set(
  preproc = list(normalized = sale_price_recipe_model_2),
  models = list(linear_reg = linear_reg_spec, random_forest = rf_spec, boosted = xgb_spec, KNN = knn_spec)
)


grid_ctrl <-
   control_grid(
      save_pred = TRUE,
      save_workflow = TRUE
   )

sales_samples <- 
   vfold_cv(train_sales_2, repeats=1, v=3) 


grid_results <-
   my_set %>%
   workflow_map(
      seed = 1503,
      resamples = sales_samples,
      grid = 15,
      control = grid_ctrl,
      verbose = FALSE
   )

# grid_results %>%
#    rank_results()

best_results <-
   grid_results %>%
   extract_workflow_set_result("normalized_KNN") %>%
   select_best(metric = "rmse")
best_results
 
best_results_fit <-
   grid_results %>%
   extract_workflow("normalized_KNN") %>%
   finalize_workflow(best_results) %>%
   last_fit(split = split_sales_model_2)


best_results_fit %>% 
   collect_predictions() %>% 
   ggplot(aes(x = sale_price, y = .pred)) + 
   geom_abline(color = "gray50", lty = 2) + 
   geom_point(alpha = 0.5) + 
   coord_obs_pred() + 
   labs(x = "observed", y = "predicted")

autoplot(
   grid_results,
   rank_metric = "rmse",  # <- how to order models
   metric = "rmse",       # <- which metric to visualize
   select_best = TRUE     # <- one point per workflow
) +
   geom_text(aes(y = mean - 1/2, label = wflow_id), angle = 90, hjust = 1) +
   lims(y = c(3.5, 9.5)) +
   theme(legend.position = "none")
```


   
   
# Hyperparameter Exploration for Classification (Part B)
   
   
```{r overassessed-hyperparameter-exploration}
overassessed_samples <-
   vfold_cv(train_model_2, repeats=1, v=3)

svm_spec <-
  svm_rbf(cost = tune(), rbf_sigma = tune()) %>%
  set_engine("kernlab") %>%
  set_mode("classification")

svm_wflow <-
  workflow() %>%
  add_model(svm_spec) %>%
  add_recipe(overassessed_second_recipe)

perf_meas <- metric_set(roc_auc, mn_log_loss)

# What sort of metrics are appropriate here? Is the ROC and the MN Log Loss appropriate starting points?

initial_vals <-
  svm_wflow %>%
  tune_grid(
    overassessed_samples,
    grid = 4,
    metrics = perf_meas
  )

ctrl <- control_bayes(verbose = TRUE)

your_search <-
  svm_wflow %>%
  tune_bayes(
    resamples = overassessed_samples,
    metrics = perf_meas,
    initial = initial_vals,
    iter = 10,
    control = ctrl
  )

#show_best(your_search)

best_results <- 
  your_search %>% 
  select_best()

model_fit <- 
  svm_wflow %>% 
  finalize_workflow(best_results) %>% 
  fit_resamples(overassessed_samples, control=control_resamples(save_pred = TRUE))
 
model_fit

```

# Conclusion (Part C)




Paragraph 1:
- Lots of injustice in Detroit
- Deserves good model

After exploring Detroit's data model, it's clear the

Paragraph 2:
- Developed models of glm for classification and for predicting sale price.
- Pretty poor models :/ 

Paragraph 3:
- When evaluating some further models, it looks like KNN was the best model that I was able to test; it produced better outcomes.
- I do not think Detroit should use my models

Paragraph 4: 
- Right now, Detroit's models are extremely poor and are causing a lot of harm.
- However, I think there are significant ethical concerns with the work I did that make it a bad idea for Detroit's assessor to adopt my model specifically.
- First of all, I have low personal stakes in this project and am not a professional; we should have evidence-based reasons to support.
- Secondly, the data is poor. While evaluating years where we know the answer, we know we are not very successful... We know harm is currently beging caused; what harm could be caused by training our data on a harmful housing market (capitalism!) and on racist patterns of valuing homes. We should exercise extreme caution in applying ML models based on this background.
- Third, I think that the use of machine learning should be a decision made by people in elected office, since the results and implications of those decisions should, in a healthy democracy, be forced to... 











