---
title: "Part 3"
author: "Jane Huber"
date: "3/3/2022"
output:
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    theme: sandstone
    number_sections: true
---

Data Setup: Add in latitude and longitude so that we have this info for later

Part A TODO (max 30 minutes on Sunday):
() Sentences for both of my models in part 1
() Remove the bad tables for the second model (metric/estimator/estimate)
() Update the grid with the two graphs to be vertical
() Tidy up all of the sentences. 

Part B TODO:
() Need to create a second predictor. (maybe "Sale price per square foot for neighborhood")
() Create a table for my results of the model, compare the two models... Need a format for this.
() Follow this for my second model (sale price model).

Part C TODO: 
() Simple out-of-sample prediction. We got data from 2016; so now we should try and predict for other years. Second model was 2019... Do we have any later years I can check (2020 for sale price???)

Part D TODO:
() Leaflet map by census tract for model A: https://juliasilge.com/blog/using-tidycensus/
() Model B maybe needs something like this: https://www.tmwr.org/explain.html#software-for-model-explanations

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(cmfproperty)
library(purrr)
library(gridExtra)
library(ggplot2)
library(readxl)
library(tidymodels)
library(glmnet)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, verbose = FALSE)

theme_set(theme_bw())
```

```{r download-data-and-clean, include=FALSE}


custom_theme <- theme_bw() +
  theme(plot.title = element_text(size = 9),
        axis.title.x = element_text(size = 9),
        axis.title.y = element_text(size = 9))

# property_classifications <- read_xlsx("files/OFFICE OF THE ASSESSORS_PROPERTY CLASSIFICATIONS -rev.xlsx")

years_for_evaluation <- c('2016', '2017', '2018', '2019')

con <- DBI::dbConnect(RSQLite::SQLite(), "../database/detroit.sqlite")

# convert to tibble
sales <- dplyr::tbl(con, 'sales') %>% dplyr::collect()

#remove factor for sale date
sales_clean <- 
  sales %>% 
  select(c(parcel_num, sale_date, sale_price, sale_terms, property_c)) %>% 
  rename(c(prop_class = property_c)) %>% 
  mutate(sale_date = format(as.Date(sale_date), format="%Y"),
         sale_terms = str_replace_all(sale_terms, "Not Arms Length", "NOT ARMS LENGTH"),
         sale_terms = str_replace_all(sale_terms, "not arms length", "NOT ARMS LENGTH"),
         sale_terms = str_replace_all(sale_terms, "valid arms length", "VALID ARMS LENGTH"),
         sale_terms = str_replace_all(sale_terms, "Valid Arms Length", "VALID ARMS LENGTH"),
         sale_terms = str_replace_all(sale_terms, "bank sale used", "BANK SALE USED"),
         sale_terms = str_replace_all(sale_terms, "00-NOT AUDITED", "NOT AUDITED"),
         prop_class = as_factor(prop_class), 
         sale_terms = as_factor(sale_terms)) %>% 
  filter(sale_terms == "VALID ARMS LENGTH",
         sale_date %in% years_for_evaluation,
         prop_class == '401')

rm(sales)
gc()

# Assessments
assessments <- dplyr::tbl(con, 'assessments') %>% dplyr::collect()

assessments_clean <-
  assessments %>%
  rename(c(parcel_num = PARCELNO,
           assessed_value = ASSESSEDVALUE,
           taxable_value = TAXABLEVALUE,
           assessment_year = year,
           prop_class = propclass)) %>% 
  mutate(prop_class = as_factor(prop_class)) %>% 
  filter(assessed_value > 2000)

rm(assessments)
gc()

# Parcels: Create a parcels tibble that combines historic with all. Can filter down later if needed.
parcels <- dplyr::tbl(con, 'parcels') %>% dplyr::collect()

parcels_current_clean <-
  parcels %>%
  rename(parcel_num = parcel_number) %>%
  mutate(zip_code = as.numeric(zip_code),
         property_class = as.factor(property_class))

rm(parcels)
gc()

parcels_historic <- dplyr::tbl(con, 'parcels_historic') %>% dplyr::collect()

parcels_historic_clean <-
  parcels_historic %>%
  rename(parcel_num = PARCELNO,
         address = PROPADDR,
         zip_code = ZIPCODE,
         taxpayer_1 = TAXPAYER1,
         taxpayer_street = TAXPADDR,
         taxpayer_city = TAXPCITY,
         taxpayer_state = TAXPSTATE,
         taxpayer_zip = TAXPZIP,
         property_class = propclass,
         tax_status = TAXSTATUS,
         total_square_footage = TOTALSQFT,
         total_acreage = TOTALACREAGE,
         frontage = FRONTAGE,
         homestead_pre = PRE,
         sale_price = SALEPRICE,
         sale_date = SALEDATE,
         assessed_value = ASSESSEDVALUE,
         taxable_value = TAXABLEVALUE) %>%
  mutate(zip_code = as.numeric(zip_code),
         property_class = as.factor(property_class)) %>% 
  filter(!is.na(total_square_footage))

rm(parcels_historic)
gc()

parcels_clean <-
  left_join(parcels_current_clean, parcels_historic_clean) %>% 
  select(c(ward, parcel_num, council_district, zip_code, total_square_footage, X, Y)) %>% 
  mutate(zip_code = as.numeric(zip_code))

rm(list='parcels_current_clean', 'parcels_historic_clean')
gc()

#Attributes
attributes <- dplyr::tbl(con, 'attributes') %>% dplyr::collect()
attributes_clean <- 
  attributes %>% 
  rename(neighborhood = Neighborhood,
         total_square_footage = total_squa,
         assessed_value = assessed_v,
         taxable_value = taxable_va,
         sale_price = 'Sale Price',
         sale_date = 'SALE_YEAR',
         total_floors = total_floo,
         prop_class = property_c) %>% 
  select(!c(st_num, st_name, taxpayer_1, use_code_d, homestead_, 'Sale Date', heightcat, Longitude, Latitude))  %>% 
  mutate(prop_class = as_factor(prop_class))

rm(attributes)
gc()


# Combine sales and assessments
sales_and_assessments <- 
  left_join(sales_clean, assessments_clean) %>% 
  filter(!is.na(sale_date)) %>% 
  mutate(sale_date = as.numeric(sale_date))

rm(list='sales_clean', 'assessments_clean')
gc()

#Combine sales, assessments, parcels
sales_assessments_parcels <- 
  left_join(sales_and_assessments, parcels_clean) 

rm(list='sales_and_assessments', 'parcels_clean')
gc()


sales_assessments_parcels_attributes <- 
  left_join(sales_assessments_parcels, attributes_clean)

rm(list='sales_assessments_parcels', 'attributes_clean')
gc()
  
#Foreclosures
foreclosures <- dplyr::tbl(con, 'foreclosures') %>% dplyr::collect()
foreclosures_clean <- 
  foreclosures %>% 
  rename(address = prop_addr,
         parcel_num = prop_parcelnum) %>% 
  select(c(address, parcel_num, years_for_evaluation)) %>% 
  pivot_longer(cols = years_for_evaluation,
               names_to = "foreclosure_year",
               values_to = "foreclosed",
               values_drop_na = TRUE) %>% 
  select(parcel_num, foreclosed)

rm(foreclosures)
gc()

#Finally create full dataset

full_dataset <- 
  left_join(sales_assessments_parcels_attributes, foreclosures_clean)

rm(list='sales_assessments_parcels_attributes', 'foreclosures_clean')
gc()

#Final cleanup--remove initial tibbles from SQLite now that we've filtered for the data we actually want

rm(list = 'con', 'years_for_evaluation')
gc()

```


# Part A

Homes in Detroit have suffered from poorly assessed home values, which has contributed greatly to foreclosure during a time of economic instability. The UC Irvine Law Review's ["Taxed Out: Illegal Property Tax Assessments and the Epidemic of Tax Foreclosures in Detroit"](https://scholarship.law.uci.edu/ucilr/vol9/iss4/3/) analyzes  the relationship between over-assessing a home and its role in driving foreclosures, exposing government's role in creating conditions for people to lose their homes. The Harris School of Public Policy at the University of Chicago's The Center For Municipal Finance produced the report ["An Evaluation of Residential Property Tax Assessments in the City of Detroit, 2016-2018"](https://harris.uchicago.edu/files/evalrespropertytaxasdetroit20162018.pdf) shows how the city of Detroit attempted to correct that mistake, reducing the number of assessments higher than sales, but that it's still too high.

Detroit’s assessment values across percentile home values appear to have remained steady in dollars since 2016, even as home assessments increased over time. It is important to note, however, that the red line (homes at the 25th percentile of sale price) have the smallest gap between their assessed value and their sale price. This helps us to see the way in which inequality has been exacerbated by assessing homes at a much closer value to their sale price than for more expensive homes.

```{r cmfproperty-sales-ratio, message = FALSE, warning = FALSE, echo = FALSE, verbose = FALSE}
ratios <-
  cmfproperty::reformat_data(
    data = full_dataset,
    sale_col = "sale_price",
    assessment_col = "assessed_value",
    sale_year_col = "sale_date",
  )

stats <- cmfproperty::calc_iaao_stats(ratios)

output <- diagnostic_plots(stats,
                           ratios,
                           min_reporting_yr = 2016,
                           max_reporting_yr = 2019)

grid.arrange(output[[3]], output[[2]], ncol = 2)

rm(list = 'stats', 'ratio', 'output')
invisible(gc())

```

Let's construct a model to determine whether or not a home was overassessed in 2016. We will use logistic regression to help us predict whether something will be "overassessed" or "underassessed". In Detroit, homes are assessed at 50% value--meaning that if a home was sold for \$100,000, it would be assessed for $50,000.  

```{r first-model-overassessment, include=TRUE}

# Get data filtered
overassessed <- 
full_dataset %>% 
  filter(sale_date == 2016,
         assessment_year == 2016) %>% 
  mutate(overassessed = as_factor(if_else(sale_price < (assessed_value * 2),
                                "YES",
                                "NO")))

split <- rsample::initial_split(overassessed)

train <- training(split)
test <- testing(split)

log_model <- 
  logistic_reg() %>%
  set_engine('glm') %>%
  set_mode('classification')

overassessed_first_recipe <- 
  recipe(overassessed ~ sale_price + ward + zip_code + total_square_footage,
      data = train) %>%
  step_other(ward, threshold = 0.01) %>% 
  step_other(zip_code, threshold = 0.01) %>% 
  step_unknown(all_nominal_predictors()) %>%
  step_dummy(all_nominal_predictors())
  
overassessed_workflow <- 
  workflow() %>%
  add_model(log_model) %>% 
  add_recipe(overassessed_first_recipe)


#Evaluate model
rf_fit <- fit(overassessed_workflow, overassessed)

homes_2016 <- 
  test %>% 
  filter(sale_date == 2016)

overassessment_predictions <- 
  augment(rf_fit, homes_2016)

rm(list='rf_fit', 'homes_2016')

overassment_evaluation <- 
  left_join(overassessment_predictions, overassessed) %>% 
  group_by(overassessed) %>% 
  summarize(predicted_not_overassessed = sum(.pred_class == "NO", na.rm=TRUE),
            predicted_overassessed = sum(.pred_class == "YES", na.rm = TRUE))

overassment_evaluation


# Create a classifier metrics table to help us further evaluate our model.

true_negative <- overassment_evaluation$predicted_not_overassessed[1]
false_negative <- overassment_evaluation$predicted_not_overassessed[2]
false_positive <- overassment_evaluation$predicted_overassessed[1]
true_positive <- overassment_evaluation$predicted_overassessed[2]

true_positive_rate <- true_positive / (true_positive + false_negative)
true_negative_rate <- true_negative / (true_negative + false_positive)
false_positive_rate <- false_positive /(false_positive + true_negative)
false_negative_rate <- false_negative / (false_negative + true_positive)
positive_predictive_value <- true_positive / (true_positive + false_positive)

classifier_metrics_table <- tibble(measurement = c("true positive rate", 
                                                   "true negative rate",
                                                   "false positive rate",
                                                   "false negative rate",
                                                   "positive predictive value"), 
                                   value = c(true_positive_rate, 
                                               true_negative_rate,
                                               false_positive_rate,
                                               false_negative_rate,
                                               positive_predictive_value))

classifier_metrics_table


```

```{r first-model-sales-predictions}

split_sales <- rsample::initial_split(full_dataset)

train_sales <- training(split_sales)
test_sales <- testing(split_sales)

linear_model_sales <- 
  linear_reg() %>% 
  set_engine("lm") 

sale_price_recipe <- 
  recipe(sale_price ~ ward + zip_code + assessed_value,
      data = train_sales) %>%
  step_other(ward, threshold = 0.01) %>% 
  step_other(zip_code, threshold = 0.01) %>% 
  step_unknown(all_nominal_predictors()) %>%
  step_dummy(all_nominal_predictors())
  
sale_wflow <- 
  workflow() %>%
  add_model(linear_model_sales) %>% 
  add_recipe(sale_price_recipe)

# Fit the model
rf_fit_sales <- fit(sale_wflow, train_sales)

rf_fit_sales %>% tidy() %>% view()

sales_2019 <- 
  test_sales %>% 
  filter(sale_date == 2019)

sale_price_predictions <- 
  augment(rf_fit_sales, sales_2019)

```

Now that we have run the model, we will use MAPE as a first evaluation.
```{r mape-analysis}

#I don't understand why I'm getting an Infinite value here...
yardstick::mape(sale_price_predictions,
     truth = sale_price,
     estimate = .pred)
```

Next, we will use RMSE to further evaluate the model.

```{r rmse-analysis}
yardstick::rmse(sale_price_predictions,
     truth = sale_price,
     estimate = .pred)

```

# Part B

```{r second-model-overassessment-and-comparison}

neighborhood_foreclosure_percentage <- 
  full_dataset %>% 
  filter(!is.na(zip_code)) %>% 
  group_by(zip_code) %>% 
  summarise(percent_zip_foreclosures = sum(foreclosed, na.rm=TRUE)/n(),
            avg_sale_price_zip = mean(sale_price, na.rm=TRUE))

overassessed_with_additional_field <- 
  left_join(overassessed, neighborhood_foreclosure_percentage)

split_2 <- rsample::initial_split(overassessed_with_additional_field)

train_model_2 <- training(split_2)
test_model_2 <- testing(split_2)

# Add new field here 
overassessed_second_recipe <- 
  recipe(overassessed ~ percent_zip_foreclosures + avg_sale_price_zip + ward + sale_price + zip_code + total_square_footage,
      data = train_model_2) %>%
  step_other(ward, threshold = 0.01) %>% 
  step_other(zip_code, threshold = 0.01) %>% 
  step_unknown(all_nominal_predictors()) %>%
  step_dummy(all_nominal_predictors())


#use old workflow with model, just remove old recipe and add new one
overassessed_workflow <- 
  overassessed_workflow %>% 
  update_recipe(overassessed_second_recipe)

rf_fit_model_2 <- 
  fit(overassessed_workflow, overassessed_with_additional_field)

homes_2016_model2 <- 
  test_model_2 %>% 
  filter(sale_date == 2016)

overassessment_predictions_model_2 <- 
  augment(rf_fit_model_2, homes_2016_model2)


overassment_evaluation_model_2 <- 
  left_join(overassessment_predictions_model_2, overassessed) %>% 
  group_by(overassessed) %>% 
  summarize(predicted_not_overassessed = sum(.pred_class == "NO", na.rm=TRUE),
            predicted_overassessed = sum(.pred_class == "YES", na.rm = TRUE))

overassment_evaluation_model_2


# Create a classifier metrics table to help us further evaluate our model.

true_negative <- overassment_evaluation_model_2$predicted_not_overassessed[1]
false_negative <- overassment_evaluation_model_2$predicted_not_overassessed[2]
false_positive <- overassment_evaluation_model_2$predicted_overassessed[1]
true_positive <- overassment_evaluation_model_2$predicted_overassessed[2]

true_positive_rate <- true_positive / (true_positive + false_negative)
true_negative_rate <- true_negative / (true_negative + false_positive)
false_positive_rate <- false_positive /(false_positive + true_negative)
false_negative_rate <- false_negative / (false_negative + true_positive)
positive_predictive_value <- true_positive / (true_positive + false_positive)

classifier_metrics_table <- tibble(measurement = c("true positive rate", 
                                                   "true negative rate",
                                                   "false positive rate",
                                                   "false negative rate",
                                                   "positive predictive value"), 
                                   value = c(true_positive_rate, 
                                               true_negative_rate,
                                               false_positive_rate,
                                               false_negative_rate,
                                               positive_predictive_value))

classifier_metrics_table

rm(list='true_negative', 'false_negative', 'false_positive', 'true_positive',
   'true_positive_rate',
   'true_negative_rate',
   'false_positive_rate',
   'false_negative_rate',
   'positive_predictive_value')
gc()


```
This model is better, but not by much.


